Predicting Solid State Material Platforms for Quantum Technologies

### 2022-02-27 paper_v2.tex
Updates from Overleaf

The principal components that are deemed important by the three approaches are distinct on multiple levels. The Ferrenti and extended Ferrenti approaches place particular value on the band gap, of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding. Notably, these features were used as guidance in the initial selection process when forming the training sets. Thus, the ML methods appear to preserve the criteria imposed in the Ferrenti approaches. For the empirical approach, we did not guide the selection process in terms of specific properties, thus, other properties dominate. Rather than focusing on, e.g., the band gap, the ML methods appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component. In this approach, the ML methods appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.

\subsection*{Predicting Suitable Material Hosts for Quantum Technology} 
%In this section, 
After training the machine learning approaches using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches. 
An overview of the number of predicted suitable candidates as a function of a given machine learning approach's confidence is summarized in Table~\ref{tab:probabilites}.

\begin{table}[t]
    \centering 
    \caption{Overview of the number of predicted suitable candidates as a function of a given machine learning approach's confidence when the four methods in an approach agree. A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
    \begin{tabular}{c|c|c|c}
      & $0.50$ & $0.75$ & $0.85$ \\
     \hline
     Ferrenti approach &  $6804$ & $1784$ & $258$  \\
     Extended Ferrenti approach &  $9227$ & $4735$  & $2001$  \\ 
     Empirical approach & $214$ & $66$ & $9$ \\
     \hline
     All approaches together & $47$ & $6$ & 0 \\
    \end{tabular}
    \label{tab:probabilites}
\end{table}

@@

Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$. 
The nine materials (considering different crystal structures, see Table~\ref{tab:materialproperties}) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic. Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems using examples and  Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.  Interestingly, we find that all nine materials appear to be four-fold coordinated, and that the first two lattice vectors ($a$ and $b$) are identical in all nine cases whereas $c$ may differ.  
There appears to be a high degree of symmetry present for all materials, but we find no elemental and perfectly symmetric semiconductors in the list.

Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this a partial explanation for why the models recognize BN as a suitable candidate with high probability. Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set. 
%The element S resides in the same group as Se, and 
The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively.

@@

In the case of BC$_2$N we find two compositions with the same chemical formula; the orthorhombically coordinated (mp-$629458$) and the tetragonally structured (mp-$1008523$) BC$_2$N. The former takes on a polar space group while the latter does not. The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database. 
%BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN. 
Both structures exhibit, as expected, strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}. Importantly, the diamond-like structure of BC$_3$N was recently predicted as a prominent spin qubit material host \cite{Wang2020SpinQB}. By creating a boron (B) vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond. Whether this is also possible for BC$_2$N remains to be seen. We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.

>>>>

The principal components that are deemed important by the three approaches exhibit several differences. The Ferrenti and extended Ferrenti approaches place particular value on the band gap of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding. Notably, these features were used as guidance in the initial selection process when forming the training sets. Thus, the ML methods appear to preserve the criteria imposed in the Ferrenti approaches. For the empirical approach, we did not guide the selection process in terms of specific properties, thus, other properties dominate. Rather than focusing on, e.g., the band gap, the ML methods appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component. In this approach, the ML methods appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.

\subsection*{Predicting Suitable Material Hosts for Quantum Technology} 
%In this section, 
After training the machine learning approaches using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches (Ferrenti, extended Ferrenti and empirical). 
An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in Table~\ref{tab:probabilites}.

\begin{table}[t]
    \centering 
    \caption{Overview of the number of predicted suitable candidates as a function of a given ML method's confidence when the four methods in an approach agree. A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
    \begin{tabular}{c|c|c|c}
      & $0.50$ & $0.75$ & $0.85$ \\
     \hline
     Ferrenti approach &  $6804$ & $1784$ & $258$  \\
     Extended Ferrenti approach &  $9227$ & $4735$  & $2001$  \\ 
     Empirical approach & $214$ & $66$ & $9$ \\
     \hline
     All approaches together & $47$ & $6$ & 0 \\
    \end{tabular}
    \label{tab:probabilites}
\end{table}

@@

Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$. 
The nine materials (considering different crystal structures, see Table~\ref{tab:materialproperties}) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic. Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems. Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.  Interestingly, we find that all nine materials appear to be four-fold coordinated, and that the first two lattice vectors ($a$ and $b$) are identical in all nine cases whereas $c$ may differ.  
There appears to be a high degree of symmetry present for all materials, but we find no elemental and perfectly symmetric semiconductors in the list.

Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the models recognize BN as a suitable candidate with high probability. Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set. 
%The element S resides in the same group as Se, and 
The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively.

@@

In the case of BC$_2$N we find two compositions with the same chemical formula; the orthorhombically coordinated (mp-$629458$) and the tetragonally structured (mp-$1008523$) BC$_2$N. The former takes on a polar space group while the latter does not. The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database. 
%BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN. 
Both structures exhibit, as expected, a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}. Importantly, the diamond-like structure of BC$_3$N was recently predicted as a prominent spin qubit material host \cite{Wang2020SpinQB}. By creating a boron (B) vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond. Whether this is also possible for BC$_2$N remains to be seen. We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
